Moment Constraints Make Learning Latent-Variable Models Easier

### 2014-01-31 doc/icml2014/directed.tex
Added some figures and made some changes to sample complexity stuff

Applying \TensorFactorize to every bottleneck gives us candidate views
  for every hidden variable. 
To proceed, we need to show two things; (i) under what assumptions
  does \assumptionref{full-rank} hold for each bottleneck and (ii)
  that the candidate views actually imply that \propertyref{exclusive-views}
  holds for every clique in the graph.

To address the first, we will need that the following assumption on the
  parameters of the model:
\begin{assumption} 
  \label{asm:full-rank-plus}
  For every clique $\sC = \{h_{i_1}, \cdots, h_{i_m}\} \in \sG$, let
    $Z_\sC$ be the marginal distribution for that clique. 
  Then every mode-$i$ unfolding of $Z_\sC$ has full column rank.\verify
\end{assumption}
Intuitively, the assumption guarantees that the marginal probability of
  any hidden state is non-zero.

Before we establish the second condition, we describe a reduction to
  a canonical form that will allow us to handle the case where an observed
  variable has multiple parents.

@@

\LearnMarginals~ combines two consistent algorithms, \TensorFactorize and
  \LearnClique, and is thus consistent itself. Using results from
  \citet{anandkumar12moments,anandkumar13tensor} we can show that that
  learning $\mOpp{v_1}{i}$ for the bottleneck $h_i$ with views $x_{v_1},
  x_{v_2}, x_{v_3}$ has the following sample complexity,
\begin{align*}
  \|\mOpphat{v_1}{i} - \mOpp{v_1}{i}\|^2_F &= \frac{1}{\sqrt{n}} O( \frac{k {\pi\oft{i}}_{\max}^2}{\sigma_k(M_{v_1,v_2})^5} ). 
\end{align*}

We next describe the asymptotic variance for \LearnClique when using the
  method of moments.
\begin{lemma}(Asymptotic variance of $Z_\sC$)
  \label{lem:mom-variance}  
  The asymptotic variance of $Z_\sC$, $\Sigma^\mom_\sC$ is,
  \begin{align*}
    \Sigma^{(\mom)} &= \mOppit{\sV}{\sC} \Sigma_\sV \mOppi{\sV}{\sC},
  \end{align*}
  where $\pinv{\mOpp{\sV}{\sC}} \eqdef \pinv{\mOpp{v_1}{i_1}} \otimes
    \cdots \otimes \pinv{\mOpp{v_m}{i_m}}$, a $k^m \times d^m$ matrix, and 
\begin{align*}
  \Sigma_\sV &= \diag  M_\sV  - M_\sV M_\sV^T,
\end{align*}
  is the variance of the observations $M_\sV$.
\end{lemma}
\begin{proof}
We have for each clique,
\begin{align*}
  Z_{\sC} &= \mO_\sV(\mOppi{v_1}{i_1},\cdots,\mOppi{v_m}{i_m}) \\
\end{align*}

>>>>

Applying \TensorFactorize to every bottleneck gives us candidate views
  for every hidden variable, provided \assumptionref{full-rank} holds for each bottleneck;
\begin{assumption} 
  \label{asm:full-rank-plus}
  For every hidden variable $h_i$, $\pi\oft{i} \succ 0$ and
    $\mOpp{v}{i}$ has full column rank.
\end{assumption}

Next, we must show that these candidate views actually imply that
  \propertyref{exclusive-views} holds for every clique in the graph.
Before we establish this condition, we describe a reduction to
  a canonical form that will allow us to handle the case where an observed
  variable has multiple parents.

@@

\LearnMarginals~ combines two consistent algorithms, \TensorFactorize and
  \LearnClique, and is thus consistent itself. 
We next describe the asymptotic variance for \LearnClique when using the
  method of moments.
\begin{lemma}(Asymptotic variance of $Z_\sC$)
  \label{lem:mom-variance}  
  The asymptotic variance of $Z_\sC$, $\Sigma^\mom_\sC$ is,
  \begin{align*}
    \Sigma^{(\mom)} &= \mOppit{\sV}{\sC} \Sigma_\sV \mOppi{\sV}{\sC},
  \end{align*}
  where $\pinv{\mOpp{\sV}{\sC}} \eqdef \pinv{\mOpp{v_1}{i_1}} \otimes
    \cdots \otimes \pinv{\mOpp{v_m}{i_m}}$, a $k^m \times d^m$ matrix, and 
\begin{align*}
  \Sigma_\sV &= \diag  M_\sV  - M_\sV M_\sV^T,
\end{align*}
  is the variance of the observations $M_\sV$.
\end{lemma}
\begin{proof}
We have for each clique,
\begin{align*}
  Z_{\sC} &= \mO_\sV(\mOppi{v_1}{i_1},\cdots,\mOppi{v_m}{i_m}) \\
\end{align*}
